Polarized Illumination For Determining Single-Molecule Orientation: Modeling and Instrument Design

### 2017-07-07 paper/paper/paper.tex
Generate and caption single arm figure.

\begin{document}
\title{Determining Single-Molecule Orientation With Polarized Illumination:
  Instrument Design and Forward Model}

@@

\section{Introduction}

\section{Methods}
Illumination forward model, CRLB, dispersion index

\section{Results}
\subsection{One-Arm Designs}
\begin{figure}[htbp]
\centering\includegraphics[width=\textwidth]{single-frame}
\caption{Caption 123}
\end{figure}

@@

\section{Conclusion}
After proofreading the manuscript, compress your .TEX manuscript file and all
figures (which should be in EPS format, or PDF format if you are using
PDF-\LaTeX) in a ZIP, TAR or TAR-GZIP package. Prism, OSA's article tracking
system, will process in \LaTeX mode by default but will use PDF-\LaTeX if PDF
figure files are detected. Note: TAR or TAR-GZIP is no longer required. All
files must be referenced at the root level (e.g., file \texttt{figure-1.eps},
not \texttt{/myfigs/figure-1.eps}). If there is video or other multimedia, the
associated files should be uploaded separately.

>>>>

\begin{document}
\title{Polarized Illumination For Determining Single-Molecule Orientation:
  Modeling and Instrument Design}

@@

\section{Introduction}
Single molecule orientation determination is important because

A variety of techniques have been tested to determine the orientation of
single molecules:

polarized detection [Fourkas], shape analysis [Moerner], other things from
Moerner review.

We propose polarized illumination as an complementary method to polarized
detection. We get the speed (no shape analysis required).

In this work we make three contributions:
\begin{itemize}
\item we develop the polarized illumination forward model for a broad class of
  microscopes (section 2.X-2.X)
\item we develop metrics to compare the performance of polarized illumination
  microscopes 
\item we use these metrics to compare microscopes design and make recommendations
  for polarized illumination microscopes. 
\end{itemize}

\section{Methods}
\subsection{Illumination Model}

\subsection{Detection Model}

\subsection{Complete Forward Model}
\begin{align}
  I = I_{\text{tot}}\eta_{\text{exc}}\eta_{\text{det}}
\end{align}

\subsection{Microscope Designs}

\subsection{Evaluation Metrics}
\begin{align}
  F &= \sum_{i=0}^N \frac{1}{I}
  \begin{bmatrix}
    \frac{\partial^2 I}{\partial \Theta^2}&\frac{\partial I}{\partial \Theta}\frac{\partial I}{\partial \Phi}\\
    \frac{\partial I}{\partial \Theta}\frac{\partial I}{\partial \Phi}&\frac{\partial^2 I}{\partial \Phi^2}\\    
  \end{bmatrix}\\
  \sigma_{\Omega} &= \frac{\sin\Theta}{\sqrt{\text{det}\{F\}}}
\end{align}
We call $\sigma_{\Omega}$ the \emph{solid-angle uncertainty}. 
We sampled $\sigma_{\Omega}$ on 100,000 approximately equally
spaced points on the unit sphere and calculated the \emph{coefficient of variation}
$c_v$ of these points where
\begin{align}
  c_v = \frac{\sigma_{\sigma_{\Omega}}}{\mu_{\sigma_{\Omega}}}
\end{align}

\section{Results}
\subsection{One-Arm Designs}
\begin{figure}[htbp]
\centering\includegraphics[width=\textwidth]{single-arm}
\caption{\textbf{Left:} Schematic of a single-arm four-frame epi-illumination
  microscope with NA = 0.8 and $n = 1.33$. The solid and dashed lines enclose
  the illumination and detection solid angles, respectively, and the arrows
  indicate the illumination polarization orientations. \textbf{Right:} Solid
  angle uncertainty for the same microscope when $I_{\text{tot}} = 1000$
  photons. Note the regions of high uncertainty near the equator and poles
  as noted in XXX.}
\end{figure}

@@

\section{Conclusion}
